\begin{frame}
  \frametitle{Motivation}
  Are any of these phrases familiar?
  \begin{itemize}
    \pause
    \item It was working just last week!
    \pause
    \item I only made a small change, I don't know how it could have broken \emph{that}...
    \pause
    \item I'm sure I've fixed this before.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Motivation}
  Tests will save you time.
  \begin{itemize}
    \item Larger codes will have many systems.
    \item Unexpected consequences.
    \item Automation.
    \item Less debugging later.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Time: Thinking Long Term}
  \begin{tikzpicture}[overlay]
    \node[nrm,minimum width=10.7cm,anchor=north west] at (0,-3) {Library};
    \node[nrm,minimum width=5.15cm,anchor=north west] at (0,-0.5) {Application};
    \node[nrm,minimum width=5.15cm,anchor=north west] at (5.5,-0.5) {Library};
    \node[nrm,minimum width=5.15cm,anchor=north west] at (5.5,2) {Application};
    \node[single arrow,draw=none,fill=Base09,rotate=-90,anchor=north west] at (2.8,-1.9) {uses};
    \node[single arrow,draw=none,fill=Base09,rotate=-90,anchor=north west] at (8.3,-1.9) {uses};
    \node[single arrow,draw=none,fill=Base09,rotate=-90,anchor=north west] at (8.3,0.6) {uses};
  \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Motivation}
  Show stats on typical code sizes and sizes of other test suites to highlight
  time savings. Also show complexity with stats on if conditionals.
\end{frame}

\begin{frame}
  \frametitle{Motivation}
  Tests don't just idenitfy problems, they prevent them.

  What here?
\end{frame}

\begin{frame}[fragile]
  \frametitle{Motivation}
  Tests make your code more attractive.
  \epigraph{``Code without tests is broken by design.''}{--- \textup{Jacob Kaplan-Moss}, Django documentation}
\end{frame}

\begin{frame}
  \frametitle{Motivation}
  Tests help teams work together.

  If you modify someone else's code, how do you know it all still works?
\end{frame}

\begin{frame}
  \frametitle{Motivation}
  Show massive list of projects with test suites.
\end{frame}
